---
title: "Probability & Probability Distributions"
author: 
date: 
output: pdf_document
---

# Formative Assessment 4

**Name:** CALALANG, JHAN CAZHANDRA D.

**Section:** APM1110 - SECTION 2

**GitHub Link:** https://github.com/jhancazhandracalalang/CALALANG-JC-FA4/blob/main/CALALANG%2C%20JC-FA4.Rmd

# Exercise 7.1

## Item 2

A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0.

### (a) Probability that a 1 was received

Given:

- P(T = 0) = 0.70
- P(T = 1) = 0.30
- P(R = 1 | T = 0) = 0.05
- P(R = 1 | T = 1) = 0.75

Using the Law of Total Probability:

\[
P(R = 1) = P(R = 1|T = 0)P(T = 0) + P(R = 1|T = 1)P(T = 1)
\]

```{r}
P_T0 <- 0.70
P_T1 <- 0.30

P_R1_given_T0 <- 1 - 0.95
P_R1_given_T1 <- 0.75

P_R1 <- P_R1_given_T0 * P_T0 +
        P_R1_given_T1 * P_T1

P_R1
```

Therefore, the probability that a 1 was received is:

\[
\boxed{P(R = 1) = 0.26 = 26\%}
\]

### (b) Probability that a 1 was transmitted given that a 1 was received

Using Bayes' Theorem:

\[
P(T = 1|R = 1) =
\frac{P(R = 1|T = 1)P(T = 1)}
{P(R = 1)}
\]

```{r}
P_T1_given_R1 <- (P_R1_given_T1 * P_T1) / P_R1

P_T1_given_R1
```

Therefore:

\[
\boxed{P(T = 1|R = 1) \approx 0.8654 = 86.54\%}
\]

---

## Item 7

There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane's work, 5% of Amy's work, and just 1% of Ava's work is in error.

### Overall percentage of error

Given:

- P(Jane) = 0.10
- P(Amy) = 0.30
- P(Ava) = 0.60
- P(Error | Jane) = 0.08
- P(Error | Amy) = 0.05
- P(Error | Ava) = 0.01

Using the Law of Total Probability:

\[
P(Error) = P(Error|Jane)P(Jane) +
P(Error|Amy)P(Amy) +
P(Error|Ava)P(Ava)
\]

```{r}
P_Jane <- 0.10
P_Amy <- 0.30
P_Ava <- 0.60

P_Error_Jane <- 0.08
P_Error_Amy <- 0.05
P_Error_Ava <- 0.01

P_Error <- P_Error_Jane * P_Jane +
           P_Error_Amy * P_Amy +
           P_Error_Ava * P_Ava

P_Error
```

The overall percentage of error is:

```{r}
P_Error * 100
```

Therefore:

\[
\boxed{P(Error) = 0.029 = 2.9\%}
\]

### Most likely person to have written the program

Using Bayes' Theorem:

```{r}
P_Jane_given_Error <- (P_Error_Jane * P_Jane) / P_Error
P_Amy_given_Error <- (P_Error_Amy * P_Amy) / P_Error
P_Ava_given_Error <- (P_Error_Ava * P_Ava) / P_Error

P_Jane_given_Error
P_Amy_given_Error
P_Ava_given_Error
```

The probabilities are:

```{r}
P_Jane_given_Error * 100
P_Amy_given_Error * 100
P_Ava_given_Error * 100
```

Therefore:

- Jane = 27.59%
- Amy = 51.72%
- Ava = 20.69%

Since Amy has the highest probability, **Amy is the most likely person to have written the program with an error.**

\[
\boxed{\text{Amy, }51.72\%}
\]